ZCB Pricing

### 2018-07-02 ZCB Pricing .Rmd
Modified explicit method function

explicit <- function(alpha,beta,sigma,r,I,dr){

# I = partition of time
# dr = length of rate sub-intervals
# r must be in the middle of partition of J
# length of J must be twice the length of I

@@

dt = 1/length(I) # length of each time sub-interval
dr = J[2] -J[1] # length of each rate sub-interval

@@

explicit(0.01,0.1,0.04,0.10,1:20,0.005)

@@

```{r 5}
# Implicit Method
```

>>>>

explicit <- function(alpha,beta,sigma,r,I){

# I = partition of time
# J = partition of rate
# dr = length of rate sub-intervals
# r must be in the middle of partition of J
# length of J must be twice the length of I
dr <- 2*r/(2*length(I))

@@

dt = 1/length(I) # length of each time sub-interval

@@

explicit(0.01,0.1,0.04,0.05,1:10)

@@

```{r 5}
# Implicit Method
